Manuscript figures

### 2024-03-19 04_manuscript_plots.Rmd
add forecast summary

>>>>

## Summary stats
```{r}
# total forecasts
distinct_forecasts <- arrow::open_dataset("./scores_2023") |> 
  distinct(model_id, site_id, variable, reference_datetime) |> 
  collect()

# variable forecasts
distinct_forecasts |> 
  group_by(variable ) |>
  summarise(n = n()) |> 
  mutate(percent = 100*(n/nrow(distinct_forecasts)))

# lake temp forecasts
distinct_forecasts |> 
  filter(site_id %in% lake_sites,
         variable == 'temperature') |> 
  summarise(n = n()) 
```
